Results

### 2019-06-22 analysis/02_clean-data.Rmd

col_names <- names(read_csv(here::here("data", "raw_data", "conjointqsf_final.csv")))
data <- read_csv(
  here::here("data", "conjointqsf_final.csv"),
  skip = 2,
  col_names = col_names
)
```

@@

@@

```{r clean-data, warning=FALSE, message=FALSE}
data <- data_clean %>% 
  select(-c("732d72a6-25a3-4194-8416-461acae30837.1.1_CBCONJOINT":"revision_CBCONJOINT"))

write_csv(data, here("data", "derived_data", "final_data.csv"))
```

>>>>

col_names <- names(read_csv(here::here("data", "raw_data", "conjointqsf_final.csv")))
data <- read_csv(
  here::here("data", "raw_data", "conjointqsf_final.csv"),
  skip = 2,
  col_names = col_names
)
```

@@

## Remove identifying and extraneous information

```{r clean-data, warning=FALSE, message=FALSE}
data <- data_clean %>% 
  mutate(id = row_number()) %>% 
  rename(version = vers_CBCONJOINT) %>% 
  select(id, version, Q1.1:Q5.18)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
write_csv(data, here("data", "derived_data", "final_data.csv"))
```

### 2019-06-22 analysis/03_analysis.Rmd

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(ggraph)
library(ggdag)
library(here)

@@

# Load data
# results <- readRDS(here("data", "derived_data", "results.rds"))
```

@@

>>>>

# Load data and model output

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(rstan)
library(bayesplot)
library(tidybayes)
library(bayesm)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)

@@

# Specify the model to load
intercept <- 1 # Intercept-only

# Load and extract data and model output (see model-calibration.R)
if (intercept == 1) {
  run <- read_rds(here::here("analysis", "output", "model_runs", "hmnl-intercept_noncentered.RDS"))
  data <- run$data
  fit <- run$fit
}
```

@@

# Model checking

```{r model-checking, warning=FALSE, message=FALSE}
source(here::here("R", "stan_utility.R"))

# Check for divergences
check_div(fit)

# # Check the effective sample size (not working for a hierarchical model?)
# check_n_eff(fit)
# 
# # Check the Rhat statistic (not working for a hierarchical model?)
# check_rhat(fit)

# Check trace plots
fit %>%
  extract(
    inc_warmup = TRUE,
    permuted = FALSE
  ) %>%
  mcmc_trace(
    regex_pars = "Theta",
    n_warmup = 1000,
    facet_args = list(nrow = 2, labeller = label_parsed)
  )

ggsave(
  "mcmc-trace_noncentered.png",
  path = here::here("analysis", "output", "figures"),
  width = 12, height = 6, units = "in"
)
```

# Plot marginals

```{r plot-marginals, warning=FALSE, message=FALSE}
# Extract posterior draws
draws <- fit %>% 
  spread_draws(Theta[i, j]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

# Plot marginals
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
  "Financial transparency: Yes",
  "Accountability: Yes",
  str_c("Funding sources: ", c("Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")),
  str_c("Relationship with host government: ", c("Criticized by government", "Under government crackdown"))
)
draws %>% 
  mutate(
    levels = factor(
      i,
      labels = level_labels
    )
  ) %>%
  ggplot(aes(x = Theta, y = levels)) + 
  geom_halfeyeh(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Attribute Levels")

# Save plot
ggsave(
  "marginal_posteriors.png",
  path = here::here("analysis", "output", "figures"),
  width = 12, height = 6, units = "in"
)
```
